Why is Stochastic Lambda > Deterministic?

### 2022-05-03 notes/understanding stochastic lambda.Rmd
finished notes after updating ipmr

```{r warning=FALSE}
ipm_stoch_ff <- 
  proto_ipm_stoch_ff %>%
  make_ipm(iterations = 1000,
           normalize_pop_size = FALSE, # to run as PVA
           usr_funs = list(get_scat_params = get_scat_params))

ipm_stoch_cf <- 
  proto_ipm_stoch_cf %>%
  make_ipm(iterations = 1000,
           normalize_pop_size = FALSE, # to run as PVA
           usr_funs = list(get_scat_params = get_scat_params))
```

>>>>

```{r}
year_seq = sample(c(2001, 2003), size = 1000, replace = TRUE)
```

```{r warning=FALSE}
ipm_stoch_ff <- 
  proto_ipm_stoch_ff %>%
  make_ipm(iterations = 1000,
           normalize_pop_size = FALSE, # to run as PVA
           kernel_seq = as.character(year_seq),
           usr_funs = list(get_scat_params = get_scat_params))

ipm_stoch_cf <- 
  proto_ipm_stoch_cf %>%
  make_ipm(iterations = 1000,
           normalize_pop_size = FALSE, # to run as PVA
           kernel_seq = as.character(year_seq),
           usr_funs = list(get_scat_params = get_scat_params))
```
